Finding the True MVP

### 2024-12-12 paper/paper.qmd
Small Fix
References edit

library(tidyverse)
library(rstanarm)
library(dplyr)
library(janitor)
library(lubridate)
library(modelsummary)
library(knitr)
library(StanHeaders)
library(kableExtra)

@@

We use the statistical programming language R [@citeR] along with several packages to clean and manipulate our data, including [@tidyverse], [@rstanarm], [@dplyr], [@janitor], [@lubridate], [@modelsummary], [@knitr], [@StanHeaders], and [@kableExtra]. These tools allowed us to clean the data, add years to datasets that only included basketball seasons, and generate well-formatted tables that go beyond the basic functionality of traditional R software.

@@

The panel of voters is not a random sample of all stakeholders in the NBA community. Instead, it is a curated group of media professionals, which may underrepresent certain perspectives, such as fans, coaches, or analytics experts. This introduces a potential sampling bias that could influence the results. For example, regional biases might favor players from large-market teams, while recency bias could elevate players with late-season surges. Simulation studies could explore the extent of these biases by randomly reweighting votes or introducing new voter segments, e.g., analytics specialists.

##Simulation of MVP Voting Under Different Scenarios

>>>>

library(tidyverse)
library(rstanarm)
library(janitor)
library(lubridate)
library(modelsummary)
library(knitr)
library(StanHeaders)
library(tinytable)

@@

We use the statistical programming language R [@citeR] along with several packages to clean and manipulate our data, including [@tidyverse], [@rstanarm], [@dplyr], [@janitor], [@lubridate], [@modelsummary], [@knitr], [@StanHeaders], and [@tiny]. These tools allowed us to clean the data, add years to datasets that only included basketball seasons, and generate well-formatted tables that go beyond the basic functionality of traditional R software.

@@

The panel of voters is not a random sample of all stakeholders in the NBA community. Instead, it is a curated group of media professionals, which may underrepresented certain perspectives, such as fans, coaches, or analytics experts. This introduces a potential sampling bias that could influence the results. For example, regional biases might favor players from large-market teams, while recency bias could elevate players with late-season surges. Simulation studies could explore the extent of these biases by randomly reweighting votes or introducing new voter segments, e.g., analytics specialists.

## Simulation of MVP Voting Under Different Scenarios
